Detection and Classification of Supernova Gravitational Waves Signals: A Deep Learning Approach

### 2020-04-17 Response_to_PRD_reviewers.txt

* [Fig. 9a] TAP_HLVK and TAP_H+L+VK as a function of distance between
0.5kpc - 20kpc at FAP=0.1%, 0.01%, and 0.001%

* [Fig. 9b] TAP_HLVK and TAP_H+L+VK as a function of distance between
0.5kpc - 200kpc at FAP=0.1%, 0.01%, and 0.001%

Looking at Fig. 7, however, I question if it is possible to achieve
such low FAPs with this pipeline, particularly for the neutrino
mechanism waveforms. It would be useful to remake this figure at
distances for which FAP << 0.3% is possible. If not possible, it may
be beneficial to remove the figure. If not removed, the caption and
text should be updated to note the large FAPs used.

Response: We have tested again the trained CNN with 1.08^6 test samples 
          for each distance so that we can achieved a FAP of 0.1%, 0.01% 
          and 0.001%.

          We appreciate that re-running the simulations at closer
          distances is advised, but doing so would be very 
          computationally expensive.

          The changes in response to this comment includes: 
          1. The plots in the section of results 
             (section IV and section V) have been updated.
             The text in these two sections are rewritten.

          2. Only TAP values at FAP equal to 0.1% are qouted in the      
             abstract and the conclusion. No detection claim is made for 
             FAP higher than 0.1%. The text in the abstract and the 
             conclusion has also been modified to accommodate the changes.

          3. We retracted claims regarding the ability of the 
             networks in detecting Galactic events where the explosion 
             mechanism is the neutrino-driven mechanism.

@@

          4. number of training/test samples in the last paragraph of 
             section III has been updated to be consistent with 
             this change.

          5. We would also like to highlight the fact that the plots
             previously submitted as Fig. 9a and Fig. 9b were actually 
             duplicates of previous Fig. 6a and Fig. 6b by accident. 
             Although this mistake was naturaly corrected when we updated
             the results, we would still like to bring this mistake to the
             reviewers' attention.

Overall, the study is a novel and interesting work. It is crucial,
however, to put the authors' pipeline through more rigorous testing
(i.e. at realistic FAPs, perhaps using realistic noise) before stating
its ability to detect GWs from Galactic CCSNe. I would suggest framing
instead the paper as a follow-up pipeline, but take note that the
authors explicitly distinguish their pipeline from that shown in a
similar work by Astone+2018 as designed to take time series directly
from the detectors and find signals, rather than analyzing triggers
found by some external detection pipeline. Given this, it seems
appropriate for appreciable corrections to the text and results to be
requested.

Response: We appreciate this comment and admit that testing/training 
          the CNN using realistic noise would indeed show a more 
          realistic results.
          However, such extension of the current work would require 
          a whole new set of treatments that is beyond the current scope
          of this work. 
          We therefore updated our results with more realistic 
          values of FAP and leave tests using realistic noise for future 
          work.

@@

Response: As stated above, we have updated section IV and section V.

V: Waveforms Excluded From Training

As for the results section, I suggest reruns using parameters
highlighted above, and the text subsequently rewritten to reflect the
updated results. Similarly to before, at the very least a disclaimer
on the FAPs must be added, and detection statements for FAP>0.3%
removed.

Response: As stated above, we tested again the trained CNN with 
          1.08 * 10^6 test samples to achieve FAP values of 0.1%, 0.01%, 
          0.001% as was done for section IV. The text and plots 
          are also updated to reflect this change. 
          Claims regarding the ability of the networks in detecting 
          Galatic CCSN signals if the explosion mechanism is the 
          neutrino driven mechanism are withdrawn.
